PragBat Analysis

### 2022-04-07 analysis/analysis.Rmd
run reli models

```{r}
library("papaja")
library(tidyverse)
library(knitr)
library(ggthemes)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
library(coda)
#library(ggdist)
#library(psy)
#library(tidyboot)
#library(ggpubr)
#library(blavaan)
library(brms)

@@

pf2 <- ggplot()+
  geom_hline(data = p2, aes(yintercept = chance), lty = 3)+
  geom_jitter(data = p1, aes(x = age, y = mean, pch = study), alpha = .25, width = .05, height = .01)+
  geom_smooth(data = pred, aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5, lty =study), stat = "identity", col = "black", size = 1, alpha = .25)+
  facet_wrap(~task, nrow = 2, labeller = as_labeller(task_names))+
    geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage), pch = study), position = position_dodge(width = .5))+
  labs(x = "Age", y = "Proportion correct") +
  scale_color_ptol(name = "Age group", labels = c("3-year-olds", "4-year-olds")) +
  ylim(-0.05, 1.05)+
  scale_shape_manual(values=c(1, 2, 4), name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
  scale_linetype_manual(values=c(1, 2, 3), name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
  theme_few()+
  theme(legend.position = c(.9,.225), legend.direction = "vertical", legend.box = "horizontal")+
  guides(shape = guide_legend(order = 2),linetype = guide_legend(order = 2), col = guide_legend(order = 1))

ggsave(plot = pf2,"../paper/figures/figure2.png", width = 10, height = 4, scale = 1.25)
```

@@

Here we extract and summarize the person specific $\alpha$ estimates and correalte them to performance in the card sorting and relational match-to-sample tasks.

@@

prsacor <- ggplot(rsa, aes(x = mean, y = mode))+
  #geom_abline(intercept = 2, slope = 1, lty = 2, alpha = .75)+
  geom_point(pch = 1, alpha = .75)+
  geom_smooth(method = "lm", col= "firebrick")+
  geom_text(data = cor, aes(label = label),y = 4.9, x = 0.2)+
  labs(x = "Mean proportion correct", y = "RSA model estimate (\u03b1)")+
  facet_grid(~task)+
  theme_few()

@@

Here we summarise the parameter esteimates for each test session and correlate them to get a measure of re-test reliability.

@@

ggsave(plot = prsa,"../paper/figures/figure6.png", width = 10, height = 4, scale = 1.25)
```

>>>>

```{r}
library(tidyverse)
library(knitr)
library(ggthemes)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
library(coda)
library(blavaan)
library(brms)
library(ggpubr)
library(scales)
library(tidyboot)
library(ggridges)

@@

pf2 <- ggplot()+
  geom_hline(data = p2, aes(yintercept = chance), lty = 3)+
  geom_jitter(data = p1, aes(x = age, y = mean, col = study), alpha = .25, width = .05, height = .01)+
  geom_smooth(data = pred, aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5, col =study), stat = "identity", size = 1, alpha = .25)+
  facet_wrap(~task, nrow = 2, labeller = as_labeller(task_names))+
    geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = study), position = position_dodge(width = .5))+
  labs(x = "Age", y = "Proportion correct") +
  scale_color_colorblind(name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
  ylim(-0.05, 1.05)+
  #scale_shape_manual(values=c(1, 2, 4), name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
  #scale_linetype_manual(values=c(1, 2, 3), name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
  theme_few()+
  theme(legend.position = c(.9,.225), legend.direction = "vertical", legend.box = "horizontal")
  #theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "horizontal")
  #guides(shape = guide_legend(order = 2),linetype = guide_legend(order = 2), col = guide_legend(order = 1))

ggsave(plot = pf2,"../paper/figures/figure2_2.png", width = 10, height = 4.5, scale = 1)
```

@@

Here we extract and summarize the person specific $\alpha$ estimates and correlate them to performance in the card sorting and relational match-to-sample tasks.

@@

prsacor <- ggplot(rsa, aes(x = mode, y = mean))+
  #geom_abline(intercept = 2, slope = 1, lty = 2, alpha = .75)+
  geom_point(pch = 1, alpha = .75)+
  geom_smooth(method = "lm", col= "firebrick")+
  geom_text(data = cor, aes(label = label),x = 1, y = 0.9)+
  labs(y = "Mean proportion correct", x = "RSA model estimate (\u03b1)")+
  facet_grid(~task)+
  theme_few()

@@

Here we summarize the parameter estimates for each test session and correlate them to get a measure of re-test reliability.

@@

ggsave(plot = prsa,"../paper/figures/figure6.png", width = 10, height = 4, scale = 1.25, bg = "white")
```
